Rational Monte Carlo Sampling in Trees

### 2012-01-11 paper/rmcts/paper.tex
one more small change

\begin{enumerate}
\item The $\varepsilon$-greedy allocation scheme has exponential convergencerate of the simple regret $\IE r$ (see Appendix~\ref{app:derivations-finite-eps}):
\begin{equation}
  \IE r_\varepsilon\le\sum_{j=1}^K\Delta_j\left(\frac {n\varepsilon} K + \frac {4\sqrt e}
{\Delta_j^2}\right)e^{-\Delta_j^2n\varepsilon/8K}
\end{equation}
\item The UCB allocation scheme exhibits polynomial convergence
rate (see Appendix~\ref{app:derivations-finite-ucb}):
\begin{equation}
\IE r_{ucb} \le 2\sum_{j=1}^K \Delta_jn^{\frac {-\alpha \Delta_j^2} 8}
\end{equation}
\item An asymptotic upper bound on the simple regret for the
$\varepsilon$-greedy allocation scheme non-monotonically depends on
$\varepsilon$. The lowest bound is achieved for $\varepsilon=\frac 1
2$, and for a large number of arms the bound for the $\frac 1
2$-greedy scheme approaches the square of the bound for uniform
sampling (see Appendix~\ref{app:derivations-asym-eps}).

@@

The results were empirically verified on Multi-armed Bandit instances
(Section~\ref{sec:emp-mab}), on search trees
(Section~\ref{sec:emp-mcts}), and on the sailing domain
(Section~\ref{sec:emp-sailing}), as defined in \cite{Kocsis.uct}. The
experiments confirmed the hypotheses. The algorithms used in the
experiments are:
\begin{description}
\item[RND:] uniform \underline{r}a\underline{nd}om samping;
\item[UCT:] \underline{U}pper \underline{C}onfidence Bounds applied to
  \underline{T}rees \cite{Kocsis.uct};
\item[GCT:] U\underline{CT} with the first step
  replaced with $\frac 1 2$-\underline{g}reedy sampling;
\item[QCT:] U\underline{CT} with the first step
  replaced with U\underline{Q}B.
\end{description}

>>>>

\begin{enumerate}
\item The $\varepsilon$-greedy allocation scheme has exponential convergencerate of the simple regret $\IE r$ (see Appendix~\ref{app:derivations-finite-eps}):
\begin{equation}
  \IE r_\varepsilon\le\sum_{j=1}^K\Delta_j\left(\frac {n\varepsilon} K + \frac {4\sqrt e}
{\Delta_j^2}\right)e^{-\Delta_j^2n\varepsilon/8K}
\end{equation}
\item The UCB allocation scheme exhibits polynomial convergence
rate (see Appendix~\ref{app:derivations-finite-ucb}):
\begin{equation}
\IE r_{ucb} \le 2\sum_{j=1}^K \Delta_jn^{\frac {-\alpha \Delta_j^2} 8}
\end{equation}
\item An asymptotic upper bound on the simple regret for the
$\varepsilon$-greedy allocation scheme depends \emph{non-monotonically} on
$\varepsilon$. The lowest bound is achieved for $\varepsilon=\frac 1
2$, and for a large number of arms the bound for the $\frac 1
2$-greedy scheme approaches the square of the bound for uniform
sampling (see Appendix~\ref{app:derivations-asym-eps}).

@@

The results were empirically verified on Multi-armed Bandit instances
(Section~\ref{sec:emp-mab}), on search trees
(Section~\ref{sec:emp-mcts}), and on the sailing domain
(Section~\ref{sec:emp-sailing}), as defined in \cite{Kocsis.uct}. The
experiments confirmed the hypotheses. The algorithms used in the
experiments are:
\begin{description}
\item[RND:] uniform \underline{r}a\underline{nd}om samping;
\item[UCT:] \underline{U}pper \underline{C}onfidence Bounds applied to
  \underline{T}rees \cite{Kocsis.uct};
\item[RCT:] U\underline{CT} with the first step replaced with uniform
  \underline{r}andom sampling;
\item[GCT:] U\underline{CT} with the first step
  replaced with $\frac 1 2$-\underline{g}reedy sampling;
\item[QCT:] U\underline{CT} with the first step
  replaced with U\underline{Q}B.
\end{description}
